Errata

### 2025-04-08 tex/Manuscript-1.tex
Refactor code structure for improved readability and maintainability
Update manuscript files with chapter marks and improve section formatting for clarity
Add titles to figures and tables

\chapter{Biocrust-linked changes in soil aggregate stability along a climatic gradient in the Chilean Coastal Range}
\label{chap:manuscript1} % Label for potential cross-referencing (start page)

@@

\begin{center}
    \textbf{\huge Biocrust-linked changes in soil aggregate stability along a climatic gradient in the Chilean Coastal Range}
\end{center}
\vspace{0.2cm}
\begin{center}
    \textit{SOIL, 8, 717–731, 2022}\\
    \textit{DOI: 10.5194/soil-8-717-2022}
\end{center}
    \vspace{0.1cm}
\end{center}
    \begin{justify}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M1-Figure_1.png}
	\caption{Sampled biological soil crust for PA (a), SG (b), LC (c), and NA (d).}
	\label{fig:M1-F1-Sampled_biocrust}
\end{figure}

@@

    % --- Main Caption and Label for the entire figure ---
    \caption{Mean and standard error of soil properties for Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC) and Nahuelbuta (NA), without (BSC-) and with biocrust cover (BSC+), and the interaction of both factors. (EC = electrical conductivity, BD = bulk density, C\textsubscript{t} = total carbon, SOC = soil organic carbon, SIC = soil inorganic carbon, N\textsubscript{t} = total nitrogen, C/N = carbon to nitrogen ratio). Significant factors include Tukey's Post-hoc-Test indicated by letters on the top of the bars. Different letters represent significant differences at $p <0.05$.}
    \label{fig:M1-F2-soil_properties_panel} % Use the same descriptive label

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M1-Figure_3.png}
	\caption{Mean value and standard error of aggregate proportion for dry (a) and wet (b) sieved fractions for Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC), and Nahuelbuta (NA) for biocrust (BSC+) and non-biocrust (BSC-) treatments. Significant factors and corresponding models for response variables are included in Appendix \ref{tab:appendix_a}.}
	\label{fig:M1-F3}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M1-Figure_4.png}
	\caption{Mean and standard deviation of aggregate size distribution changes between dry and wet sieving for the sites Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC), and Nahuelbuta (NA) for biocrust (BSC+) and non-biocrust (BSC-) treatments. Error bars were, in some cases, truncated for better visualization.}
	\label{fig:M1-F4}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M1-Figure_5.png}
	\caption{Mean and standard error of aggregate stability indexes for Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC),
    and Nahuelbuta (NA) for biocrust (BSC+) and non-biocrust (BSC-) treatments. $\Delta$MWD=difference in mean weight diameter,
    $\Delta$GMD=difference in geometric mean diameter, WSAR=water stability aggregate ratio, R\textsubscript{<\SI{2}{\milli\meter}}=ratio of aggregates less than \SI{2}{\milli\meter}. Significant factors and corresponding models for response variables are included in Appendix \ref{tab:appendix_a}.}
	\label{fig:M1-F5}
\end{figure}

@@

\begin{table}[htbp] % [htbp] placement specifier (Here, Top, Bottom, Page)
\centering % Center the table on the page
\caption{Appendix A. Significant factors for response variables based on generalized linear models. Models with significant interaction also include the predictors as simple parameters based on marginality principle. \\ % Line break in caption
\textit{(p-value $\le$ 0: "***"; p-value $\le$ 0.001: "**"; p-value $\le$ 0.01: "*")}} % Significance key (using <= for clarity)
\label{tab:appendix_a} % Label for cross-referencing
\begin{tabular}{@{}lllll@{}} % Left-aligned columns, @{} removes extra space at edges
\toprule
Dependent variable & Distribution & \multicolumn{3}{c}{Significance for independent variable} \\
\cmidrule(lr){3-5} % Rule under the multicolumn header only (trimmed left and right)
 & (link-function for GLM) & Site & Biocrust & Site $\times$ Biocrust \\ % Use $\times$ for multiplication
\midrule
Clay	& Gaussian	& ***	& *	& \\
Silt	& Inverse Gaussian	& ***	& *	& \\
Sand	& Gaussian	& ***	& 	& \\
Fine Silt	& Tweedie	& ***	& 	& * \\
Medium silt	& Tweedie	& ***	& ***	& * \\
Coarse silt	& Tweedie	& ***	& 	&  \\
Very fine sand	& Gaussian	& ***	& 	&  \\
Fine sand	& Tweedie	& ***	& 	&  \\
Medium sand	& Gaussian	& ***	& 	&  \\
Coarse sand	& Tweedie	& ***	& 	&  \\
pH	& Gaussian	& ***	& **	&  \\
EC	& Tweedie	& ***	& 	&  \\
BD	& Gaussian	& ***	& 	& ** \\
N\textsubscript{t}	& Gamma	& ***	& 	& ** \\ % For Nt subscript
C\textsubscript{t}	& Tweedie	& ***	& **	&  \\ % For Ct subscript
C/N	& Tweedie	& ***	& **	&  \\
19.0-30.0 mm Dry	& Tweedie	& ***	& 	&  \\
9.5-19.0 mm Dry	& Tweedie	& ***	& 	& ** \\
6.7-9.5 mm Dry	& Tweedie	& ***	& 	& ** \\
4.7-6.7 mm Dry	& Tweedie	& ***	& 	& * \\
3.4-4.7 mm Dry	& Tweedie	& ***	& 	&  \\
2.0-3.4 mm Dry	& Tweedie	& ***	& 	& * \\
\textless2.0 mm Dry	& Tweedie	& ***	& 	& *** \\ % Use \textless for less than symbol
19.0-30.0 mm Wet	& Tweedie	& ***	& *	& ** \\
9.5-19.0 mm Wet	& Tweedie	& *	& **	& * \\
6.7-9.5 mm Wet	& Tweedie	& ***	& 	&  \\
4.7-6.7 mm Wet	& Tweedie	& ***	& 	&  \\
3.4-4.7 mm Wet	& Tweedie	& ***	& 	&  \\
2.0-3.4 mm Wet	& Tweedie	& ***	& 	&  \\
\textless2.0 mm Wet	& Tweedie	& ***	& *	&  \\ % Use \textless for less than symbol
$\Delta$MWD	& Gaussian	& 	& 	&  \\ % Use \Delta for Greek Delta
$\Delta$GMD	& Tweedie	& ***	& 	&  \\ % Use \Delta for Greek Delta
WSAR	& Gaussian	& 	& 	&  \\
R\textsubscript{2 mm}	& Gaussian	& ***	& *	&  \\ % Use \textless for less than symbol
\bottomrule
\end{tabular}
\end{table}

>>>>

\chapter{Biocrust-linked changes in soil aggregate stability along a climatic gradient in the Chilean Coastal Range}
\chaptermark{Manuscript 1}

\label{chap:manuscript1} % Label for potential cross-referencing (start page)

@@

\begin{center}
    \textbf{\huge Biocrust-linked changes in soil aggregate stability along a climatic gradient in the Chilean Coastal Range}
\end{center}

\begin{center}
    \textit{SOIL, 8, 717–731, 2022}\\
    \textit{DOI: 10.5194/soil-8-717-2022}
\end{center}

\begin{justify}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M1-Figure_1.png}
	\caption[Sampled biological soil crust for the study sites]{Sampled biological soil crust for PA (a), SG (b), LC (c), and NA (d).}
	\label{fig:M1-F1-Sampled_biocrust}
\end{figure}

@@

    % --- Main Caption and Label for the entire figure ---
    \caption[Values of soil properties for the study sites, without and with biocrust cover, and the interaction of both factors]{Mean and standard error of soil properties for Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC) and Nahuelbuta (NA), without (BSC-) and with biocrust cover (BSC+), and the interaction of both factors. (EC = electrical conductivity, BD = bulk density, C\textsubscript{t} = total carbon, SOC = soil organic carbon, SIC = soil inorganic carbon, N\textsubscript{t} = total nitrogen, C/N = carbon to nitrogen ratio). Significant factors include Tukey's Post-hoc-Test indicated by letters on the top of the bars. Different letters represent significant differences at $p <0.05$.}
    \label{fig:M1-F2-soil_properties_panel} % Use the same descriptive label

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M1-Figure_3.png}
	\caption[Value for aggregate proportion of dry and wet sieved fractions for the study sites for biocrust and non-biocrust treatments]{Mean value and standard error of aggregate proportion for dry (a) and wet (b) sieved fractions for Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC), and Nahuelbuta (NA) for biocrust (BSC+) and non-biocrust (BSC-) treatments. Significant factors and corresponding models for response variables are included in Appendix \ref{tab:appendix_a}.}
	\label{fig:M1-F3}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M1-Figure_4.png}
	\caption[Values of aggregate size distribution changes between dry and wet sieving for the study sites with biocrust and non-biocrust treatments]{Mean and standard deviation of aggregate size distribution changes between dry and wet sieving for the sites Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC), and Nahuelbuta (NA) for biocrust (BSC+) and non-biocrust (BSC-) treatments. Error bars were, in some cases, truncated for better visualization.}
	\label{fig:M1-F4}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M1-Figure_5.png}
	\caption[Values of aggregate stability indexes for the study sites and for biocrust and non-biocrust treatments]{Mean and standard error of aggregate stability indexes for Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC),
    and Nahuelbuta (NA) for biocrust (BSC+) and non-biocrust (BSC-) treatments. $\Delta$MWD=difference in mean weight diameter,
    $\Delta$GMD=difference in geometric mean diameter, WSAR=water stability aggregate ratio, R\textsubscript{<\SI{2}{\milli\meter}}=ratio of aggregates less than \SI{2}{\milli\meter}. Significant factors and corresponding models for response variables are included in Appendix \ref{tab:appendix_a}.}
	\label{fig:M1-F5}
\end{figure}

@@

\begin{table}[htbp] % [htbp] placement specifier (Here, Top, Bottom, Page)
\centering % Center the table on the page
\caption[Significant factors for response variables based on generalized linear models]{Appendix A. Significant factors for response variables based on generalized linear models. Models with significant interaction also include the predictors as simple parameters based on marginality principle. \\ % Line break in caption
\textit{(p-value $\le$ 0: "***"; p-value $\le$ 0.001: "**"; p-value $\le$ 0.01: "*")}} % Significance key (using <= for clarity)
\label{tab:appendix_a} % Label for cross-referencing
\begin{tabular}{@{}lllll@{}} % Left-aligned columns, @{} removes extra space at edges
\toprule
Dependent variable & Distribution & \multicolumn{3}{c}{Significance for independent variable} \\
\cmidrule(lr){3-5} % Rule under the multicolumn header only (trimmed left and right)
 & (link-function for GLM) & Site & Biocrust & Site $\times$ Biocrust \\ % Use $\times$ for multiplication
\midrule
Clay	& Gaussian	& ***	& *	& \\
Silt	& Inverse Gaussian	& ***	& *	& \\
Sand	& Gaussian	& ***	& 	& \\
Fine Silt	& Tweedie	& ***	& 	& * \\
Medium silt	& Tweedie	& ***	& ***	& * \\
Coarse silt	& Tweedie	& ***	& 	&  \\
Very fine sand	& Gaussian	& ***	& 	&  \\
Fine sand	& Tweedie	& ***	& 	&  \\
Medium sand	& Gaussian	& ***	& 	&  \\
Coarse sand	& Tweedie	& ***	& 	&  \\
pH	& Gaussian	& ***	& **	&  \\
EC	& Tweedie	& ***	& 	&  \\
BD	& Gaussian	& ***	& 	& ** \\
N\textsubscript{t}	& Gamma	& ***	& 	& ** \\ % For Nt subscript
C\textsubscript{t}	& Tweedie	& ***	& **	&  \\ % For Ct subscript
C/N	& Tweedie	& ***	& **	&  \\
19.0-30.0 mm Dry	& Tweedie	& ***	& 	&  \\
9.5-19.0 mm Dry	& Tweedie	& ***	& 	& ** \\
6.7-9.5 mm Dry	& Tweedie	& ***	& 	& ** \\
4.7-6.7 mm Dry	& Tweedie	& ***	& 	& * \\
3.4-4.7 mm Dry	& Tweedie	& ***	& 	&  \\
2.0-3.4 mm Dry	& Tweedie	& ***	& 	& * \\
\textless2.0 mm Dry	& Tweedie	& ***	& 	& *** \\ % Use \textless for less than symbol
19.0-30.0 mm Wet	& Tweedie	& ***	& *	& ** \\
9.5-19.0 mm Wet	& Tweedie	& *	& **	& * \\
6.7-9.5 mm Wet	& Tweedie	& ***	& 	&  \\
4.7-6.7 mm Wet	& Tweedie	& ***	& 	&  \\
3.4-4.7 mm Wet	& Tweedie	& ***	& 	&  \\
2.0-3.4 mm Wet	& Tweedie	& ***	& 	&  \\
\textless2.0 mm Wet	& Tweedie	& ***	& *	&  \\ % Use \textless for less than symbol
$\Delta$MWD	& Gaussian	& 	& 	&  \\ % Use \Delta for Greek Delta
$\Delta$GMD	& Tweedie	& ***	& 	&  \\ % Use \Delta for Greek Delta
WSAR	& Gaussian	& 	& 	&  \\
R\textsubscript{2 mm}	& Gaussian	& ***	& *	&  \\ % Use \textless for less than symbol
\bottomrule
\end{tabular}
\end{table}

### 2025-04-08 tex/Manuscript-2.tex
Update dissertation files and bibliography references
- Modified Dissertation.tex to include additional packages for improved referencing and table formatting.
- Updated literatur.bib with corrected publisher information, added missing article details, and revised DOI links for accuracy.
- Enhanced table formatting in Manuscript-2.tex for clarity and consistency, including adjustments to statistical significance reporting.
- Revised section title in Results_Discussion.tex for consistency in manuscript numbering and formatting.
Update manuscript files with chapter marks and improve section form

\chapter{Biocrusts as climate-dependent regulators of erosion, water and nutrient cycling}
\label{chap:manuscript2} % Label for potential cross-referencing (start page)

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M2-Figure_1.png}
	\caption{Location of the four study sites (left) relative to South America (right). From north to south: Santa Gracia (SG), Quebrada de Talca (QdT), La Campana (LC), and Nahuelbuta (NA). Bing Satellite (obtained through QuickMapServices QGIS plugin), Map data $©$2022 Microsoft.}
	\label{fig:M2-F1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M2-Figure_2.png}
	\caption{Overview of the study sites, showing the general landscape of Santa Gracia (SG) (a), Quebrada de Talca (QdT) (c), La Campana (LC) (e), and Nahuelbuta (NA) (g). Corresponding biocrusts are illustrated in photographs (b, d, f, h). Notable biocrust features include lichen-dominated communities in SG and moss-dominated communities in NA.}
	\label{fig:M2-F2}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M2-Figure_3.png}
	\caption{Construction diagram of the soil erosion flux box used in the experiment (a), general view of a plot with the presence of biocrust prior to sampling (b). (c, d) shows an installed cutting frame and the cleared and prepared soil. (e) demonstrates the setting for rainfall simulations at the Nahuelbuta (NA) study site.}
	\label{fig:M2-F3}
\end{figure}

@@

  % --- Table 1 Code (Runoff Fluxes) ---
\begin{table}[htbp] % Changed from sidewaystable
    \centering
    \footnotesize % Reduced font size for the table
    \sisetup{separate-uncertainty = true, table-align-uncertainty = true}
    \begin{threeparttable}
      \caption{Surface runoff fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. A letter-based display of Šidák correction accompanies surface runoff parameters\tnote{a}, and the significance of the studied factors is shown as a p-value and list of covariates (C\textsubscript{T}, N\textsubscript{T}: total carbon and nitrogen content). Different letters indicate statistically significant different values based on our data, ns: non-significant.}
      \label{tab:M2-runoff_fluxes}
      \setlength{\tabcolsep}{3pt} % Reduced further slightly

@@

% --- Table 2 Code (Percolation Fluxes) ---
  \begin{table}[htbp] % Changed from sidewaystable
    \centering
    \footnotesize % Reduced font size for the table
    \sisetup{separate-uncertainty = true, table-align-uncertainty = true}
    \begin{threeparttable}
      \caption{Percolating water fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. A letter-based display of Šidák correction accompanies surface runoff parameters\tnote{a}, and the significance of the studied factor is shown as a p-value and list of covariates (C\textsubscript{T}, N\textsubscript{T}: total carbon and nitrogen content). Different letters indicate statistically significant different values based on our data, ns: non-significant.}
      \label{tab:M2-percolation_fluxes}
      \setlength{\tabcolsep}{3pt} % Reduced further slightly

@@

                             S[table-format=2.2, table-figures-uncertainty=3] @{\,} c

@@

        & SG \quad BSC+  & 202 \pm 103   &        & 24.8 \pm 15 & {(ab)} & 19 \pm 18 &        & 0.7 \pm 0.5  &       \\
        & SG \quad BSC-  & 244 \pm 251   &        & 11.1 \pm 10 & {(a)}  & 18 \pm 46 &        & 7.5 \pm 27.5 &       \\
        & QdT \quad BSC+ & 148 \pm 63.9  &        & 30.5 \pm 13 & {(b)}  & 9 \pm 13  &        & 0.3 \pm 0.3  &       \\
        & QdT \quad BSC- & 202 \pm 113   &        & 15.1 \pm 13 & {(ab)} & 5 \pm 6   &        & 0.2 \pm 0.2  &       \\
        & LC \quad BSC+  & 226 \pm 223   &        & 23.5 \pm 14 & {(ab)} & 17 \pm 19 &        & 0.6 \pm 0.5  &       \\
        & LC \quad BSC-  & 241 \pm 139   &        & 21.3 \pm 14 & {(ab)} & 9 \pm 9   &        & 0.4 \pm 0.3  &       \\
        & NA \quad BSC+  & 107 \pm 35.6  &        & 91.5 \pm 28 & {(c)}  & 30 \pm 32 &        & 0.4 \pm 0.4  &       \\
        & NA \quad BSC-  & 183 \pm 234   &        & 38.5 \pm 30 & {(b)}  & 16 \pm 15 &        & 0.4 \pm 0.3  &       \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M2-Figure_4.png}
	\caption{Total carbon (C) and nitrogen (N) fluxes in sediment and water for the four study sites. Diagonal arrows represent surface runoff. Arrows pointing vertically downward represent percolation. The diagrams on the right, with a light green surface, represent the BSC+ treatments, and the one on the left represents the BSC- treatments. Grey-filled arrows correspond to C fluxes, and yellowish arrows to N. At the same time, arrows with solid borders correspond to fluxes attached to the sediments and dashed arrows correspond to fluxes dissolved in water. Each type of arrow is proportional within each group in width to the concentration of nutrients and in length to their mass.}
	\label{fig:M2-F4}
\end{figure}

>>>>

\chapter{Biocrusts as climate-dependent regulators of erosion, water and nutrient cycling}
\chaptermark{Manuscript 2}
\label{chap:manuscript2} % Label for potential cross-referencing (start page)

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M2-Figure_1.png}
	\caption[Location of the four study sites relative to South America]{Location of the four study sites (left) relative to South America (right). From north to south: Santa Gracia (SG), Quebrada de Talca (QdT), La Campana (LC), and Nahuelbuta (NA). Bing Satellite (obtained through QuickMapServices QGIS plugin), Map data $©$2022 Microsoft.}
	\label{fig:M2-F1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M2-Figure_2.png}
	\caption[Overviw of the study sites and sampled biocrusts]{Overview of the study sites, showing the general landscape of Santa Gracia (SG) (a), Quebrada de Talca (QdT) (c), La Campana (LC) (e), and Nahuelbuta (NA) (g). Corresponding biocrusts are illustrated in photographs (b, d, f, h). Notable biocrust features include lichen-dominated communities in SG and moss-dominated communities in NA.}
	\label{fig:M2-F2}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M2-Figure_3.png}
	\caption[Field experimental setup for soil erosion and rainfall simulation: construction of the flux box, plot preparation, and biocrust evaluation at Nahuelbuta (NA)]{Construction diagram of the soil erosion flux box used in the experiment (a), general view of a plot with the presence of biocrust prior to sampling (b). (c, d) shows an installed cutting frame and the cleared and prepared soil. (e) demonstrates the setting for rainfall simulations at the Nahuelbuta (NA) study site.}
	\label{fig:M2-F3}
\end{figure}

@@

  % --- Table 1 Code (Runoff Fluxes) ---
\begin{table}[htbp] % Changed from sidewaystable
    \centering
    \footnotesize % Reduced font size for the table
    \sisetup{separate-uncertainty = true, table-align-uncertainty = true}
    \begin{threeparttable}
      \caption[Surface runoff fluxes on the study sites]{Surface runoff fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. A letter-based display of Šidák correction accompanies surface runoff parameters\tnote{a}, and the significance of the studied factors is shown as a p-value and list of covariates (C\textsubscript{T}, N\textsubscript{T}: total carbon and nitrogen content). Different letters indicate statistically significant different values based on our data, ns: non-significant.}
      \label{tab:M2-runoff_fluxes}
      \setlength{\tabcolsep}{3pt} % Reduced further slightly

@@

% --- Table 2 Code (Percolation Fluxes) ---

\begin{table}[htbp] % Changed from sidewaystable
  \centering
  \footnotesize % Reduced font size for the table
  \sisetup{separate-uncertainty = true, table-align-uncertainty = true}
  \begin{threeparttable}
    \caption[Percolating water fluxes on the study sites]{Percolating water fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. A letter-based display of Šidák correction accompanies surface runoff parameters\tnote{a}, and the significance of the studied factor is shown as a p-value and list of covariates (C\textsubscript{T}, N\textsubscript{T}: total carbon and nitrogen content). Different letters indicate statistically significant different values based on our data, ns: non-significant.}
    \label{tab:M2-percolation_fluxes}
    \setlength{\tabcolsep}{3pt} % Reduced further slightly

@@

                           S[table-format=2.2, table-figures-uncertainty=4] @{\,} c

@@

      & SG \quad BSC+  & 202 \pm 103   &        & 24.8 \pm 15.0 & {(ab)} & 19 \pm 18 &        & 0.7 \pm 0.5  &       \\
      & SG \quad BSC-  & 244 \pm 251   &        & 11.1 \pm 10.0 & {(a)}  & 18 \pm 46 &        & 7.5 \pm 27.5 &       \\
      & QdT \quad BSC+ & 148 \pm 63.9  &        & 30.5 \pm 13.0 & {(b)}  & 9 \pm 13  &        & 0.3 \pm 0.3  &       \\
      & QdT \quad BSC- & 202 \pm 113   &        & 15.1 \pm 13.0 & {(ab)} & 5 \pm 6   &        & 0.2 \pm 0.2  &       \\
      & LC \quad BSC+  & 226 \pm 223   &        & 23.5 \pm 14.0 & {(ab)} & 17 \pm 19 &        & 0.6 \pm 0.5  &       \\
      & LC \quad BSC-  & 241 \pm 139   &        & 21.3 \pm 14.0 & {(ab)} & 9 \pm 9   &        & 0.4 \pm 0.3  &       \\
      & NA \quad BSC+  & 107 \pm 35.6  &        & 91.5 \pm 28.0 & {(c)}  & 30 \pm 32 &        & 0.4 \pm 0.4  &       \\
      & NA \quad BSC-  & 183 \pm 234   &        & 38.5 \pm 30.0 & {(b)}  & 16 \pm 15 &        & 0.4 \pm 0.3  &       \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M2-Figure_4.png}
	\caption[Conceptual diagram of total carbon (C) and nitrogen (N) fluxes in sediment and water for the four study sites]{Total carbon (C) and nitrogen (N) fluxes in sediment and water for the four study sites. Diagonal arrows represent surface runoff. Arrows pointing vertically downward represent percolation. The diagrams on the right, with a light green surface, represent the BSC+ treatments, and the one on the left represents the BSC- treatments. Grey-filled arrows correspond to C fluxes, and yellowish arrows to N. At the same time, arrows with solid borders correspond to fluxes attached to the sediments and dashed arrows correspond to fluxes dissolved in water. Each type of arrow is proportional within each group in width to the concentration of nutrients and in length to their mass.}
	\label{fig:M2-F4}
\end{figure}
